knit

---
title: "Synthetic Replication Fidelity Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lme4)
```

## Load Results

```{r}
results_table <- read.csv("conservative_replicability_results_jittered.csv")
```

## Summary 1: g_Diff by Sample Size and Model

```{r}
gdiff_summary <- results_table %>%
  group_by(SampleSize, Model) %>%
  summarise(
    Avg_g_Diff = round(mean(g_Diff), 3),
    Min_g_Diff = round(min(g_Diff), 3),
    Max_g_Diff = round(max(g_Diff), 3),
    .groups = "drop"
  )
gdiff_summary
```

## Summary 2: CI Overlap by Sample Size and Model

```{r}
ci_summary <- results_table %>%
  group_by(SampleSize, Model) %>%
  summarise(
    Avg_CI_Overlap = round(mean(CI_OverlapPct), 1),
    Min_CI_Overlap = round(min(CI_OverlapPct), 1),
    Max_CI_Overlap = round(max(CI_OverlapPct), 1),
    .groups = "drop"
  )
ci_summary
```

## Summary 3: Full Decision Agreement Rate

```{r}
decision_agreement <- results_table %>%
  group_by(SampleSize, Model) %>%
  summarise(
    FullAgreeRate = paste0(round(mean(FullDecisionAgree) * 100, 1), "%"),
    .groups = "drop"
  )
decision_agreement
```

## Summary 4: Z-Score Acceptability

```{r}
z_score_summary <- results_table %>%
  summarise(
    Z_Synth_Accept = paste0(round(mean(Z_Synth_Accept) * 100, 1), "%"),
    Z_Real_Accept = paste0(round(mean(Z_Real_Accept) * 100, 1), "%")
  )
z_score_summary
```

## Mixed Effects Model Summary

```{r}
lme <- lmer(g_Diff ~ SampleSize + Model + (1|Variable), data = results_table)
summary(lme)
anova(lme)
```

## Summary Paragraph

The synthetic data replication pipeline yielded high-fidelity replications of original RCT treatment effects across all metrics evaluated. Full decision agreement—matching both direction and significance—was observed in nearly all conditions, reaching 100% at all sample sizes ≥ 50. All synthetic estimates fell within the original RCT confidence intervals, confirming a conservative estimation process (EstimateDistFromCI = 0 across all 75 cases). Z-scores based on synthetic sampling distributions (Z_Synthetic) fell within ±1.96 in 100% of cases, confirming inferential validity. Hedges' g differences (g_Diff) systematically declined with increasing sample size, with BoostedTree showing the lowest average discrepancy. Confidence interval overlap also improved with sample size, with BoostedTree and RandomForest outperforming GAN at low n, but all models converging by n = 500. A linear mixed-effects model confirmed a significant effect of sample size on g_Diff, supporting the robustness of replication as data volume increases.
